### 2018-08-31 manuscript/manuscript.Rmd
right

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

@@

```{r, echo=FALSE, message=FALSE}
require(ggplot2)
require(papaja)
require(Hmisc) #for mean_cl_boot
dodg = .3
gg<-ggplot(estimates %>% filter(exclude==FALSE), 
           aes(x=orientation, y=efficacy, color=stream)) + 
          geom_point(position = position_dodge(width = dodg)) + 
  stat_summary(fun.y="mean",geom="point",size=8, alpha=.5, position = position_dodge(width = dodg)) +
  stat_summary(fun.data = mean_cl_boot, geom="errorbar", width=0.4, position = position_dodge(width = dodg)) +
  theme_apa() +ggtitle('good')
show(gg)
```

>>>>

floatsintext      : no
figurelist        : no
figsintext        : yes
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

@@

```{r, echo=FALSE, message=FALSE}
require(readr); require(dplyr)
estimates <- read_tsv(file.path("..","E1","Results",'backwards2E1_paramEstimatesWithExcludeColumn.tsv'))
require(ggplot2)
require(papaja)
require(Hmisc) #for mean_cl_boot
dodg = .3
gg<-ggplot(estimates %>% filter(exclude==FALSE), 
           aes(x=orientation, y=efficacy, color=stream)) + 
          geom_point(position = position_dodge(width = dodg)) + 
  stat_summary(fun.y="mean",geom="point",size=8, alpha=.5, position = position_dodge(width = dodg)) +
  stat_summary(fun.data = mean_cl_boot, geom="errorbar", width=0.4, position = position_dodge(width = dodg)) +
  theme_apa() 
show(gg)
```

apa_print() and apa_table() facilitate reporting results of your analyses. Take a look at the .Rmd of the example manuscript in the folder example and the resulting .pdf.

Drop a supported analysis result, such as an htest- or lm-object, into apa_print() and receive a list of possible character strings that you can use to report the results of your analysis.

my_lm <- lm(Sepal.Width ~ Sepal.Length + Petal.Width + Petal.Length, data = iris)
apa_lm <- apa_print(my_lm)
